---
title: "020520-qpcr_crabRNA"
output: html_document
---
R markdown for cleaning up Pam's qPCR results spreadsheet and joining with Crab RNA extraction spreadsheet. 

```{r}
library(dplyr)
library(tidyr)
```

#### Read in qpcr csv (taken from "all good by sample" tab in project-crab/data/Excel-data-from-Pam/20180518_Hemato_qPCR_results) 
Note: I replaced "N/A"s in the "sq" column with "0"s
```{r}
qpcr <- read.csv("../analyses/hemat_qPCR.csv")
head(qpcr)
```

Take mean of starting quantities and group by FRP number. Add to column "sq_all.runs_mean"
```{r}
qpcr <- qpcr %>%
  group_by(FRP) %>%
  mutate(sq_all.runs_mean = mean(sq))
head(qpcr)
```

write out csv for now 
```{r}
#write.csv(qpcr, "../analyses/qpcr_hemat-new.csv")
```

reduce number of column in qpcr to target, sq_all.runs_mean, sample_pos.neg, FRP
```{r}
qpcr_reduced <- select(qpcr, target, sq_all.runs_mean, sample_pos.neg, FRP)
head(qpcr_reduced)
```

remove duplicate rows
```{r}
qpcr_reduced <- distinct(qpcr_reduced)
head(qpcr_reduced)
```

read in crab RNA results
```{r}
rna <- read.csv("../analyses/crab_RNA_and_trtmnt-reducted_GAC.csv")
head(rna)
```

Join with crab RNA results
```{r}
qpcr_crabRNA <- left_join(rna, qpcr_reduced, by = "FRP")
head(qpcr_crabRNA)
```

04072021
For consistency with updated version of naming sample days, Change "9" --> "0", "12" --> "2" (note, in my original day naming, it should have been 9, 11, 26), "26" --> "17". 

df1$Sp2[df1$Sp2 == 8] <- 800

Change "9" to "0"
```{r}
qpcr_crabRNA$sample_day[qpcr_crabRNA$sample_day == 9] <- 0
head(qpcr_crabRNA)
```

Change "12" to "2"
```{r}
qpcr_crabRNA$sample_day[qpcr_crabRNA$sample_day == 12] <- 2
head(qpcr_crabRNA)
```

Change "26" to "17
```{r}
qpcr_crabRNA$sample_day[qpcr_crabRNA$sample_day == 26] <- 17
head(qpcr_crabRNA)
```

04072021:
Now, add in the sequencing ID associated with each sample, if the sample was sequenced. Some were sequenced as individuals, some were pooled. 

New file in project-crab:
```{r}
sample_rnaseq <- read.csv("../data/sample-list-RNAseq.csv")
head(sample_rnaseq)
```

```{r}
sample_rnaseq <- select(sample_rnaseq, sample_number, Library_ID)
head(sample_rnaseq)
```

Rename column 
```{r}
colnames(sample_rnaseq) <- c("tube_number", "Library_ID")
head(sample_rnaseq)
```

`join` with qpcr_crabRNA based on "tube_number":
```{r}
qpcr_crabRNA_seq <- left_join(qpcr_crabRNA, sample_rnaseq, by = "tube_number")
head(qpcr_crabRNA_seq)
```


write qpcr_crabRNA to analyses: 04072021
```{r}
write.csv(qpcr_crabRNA_seq, "../analyses/hematqpcr_crabRNA.csv", row.names = FALSE, quote = FALSE)
```
