---
title: "020520-qpcr_crabRNA"
output: html_document
---
R markdown for cleaning up Pam's qPCR results spreadsheet and joining with Crab RNA extraction spreadsheet. 

```{r}
library(dplyr)
library(tidyr)
```

#### Read in qpcr csv (taken from "all good by sample" tab in project-crab/data/Excel-data-from-Pam/20180518_Hemato_qPCR_results) 
Note: I replaced "N/A"s in the "sq" column with "0"s
```{r}
qpcr <- read.csv("../analyses/hemat_qPCR.csv")
```

Take mean of starting quantities and group by FRP number. Add to column "sq_all.runs_mean"
```{r}
qpcr <- qpcr %>%
  group_by(FRP) %>%
  mutate(sq_all.runs_mean = mean(sq))
```

write out csv for now
```{r}
write.csv(qpcr, "../analyses/qpcr_hemat-new.csv")
```

reduce number of column in qpcr to target, sq_all.runs_mean, sample_pos.neg, FRP
```{r}
qpcr_reduced <- select(qpcr, target, sq_all.runs_mean, sample_pos.neg, FRP)
```

remove duplicate rows
```{r}
qpcr_reduced <- distinct(qpcr_reduced)

```

read in crab RNA results
```{r}
rna <- read.csv("../crab_RNA_and_trtmnt-reducted_GAC.csv")
```

Join with crab RNA results
```{r}
qpcr_crabRNA <- left_join(rna, qpcr_reduced, by = "FRP")

```

write qpcr_crabRNA to analyses
```{r}

write.csv(qpcr_crabRNA, "../analyses/qpcr_crabRNA-reduced.csv")
```
