---
title: 'annotate and enrich 2019 crab: infected vs uninfected'
output: github_document
---
Rmd for annotating a list of 773 DEGs from Steven (crab data 2019 - comparing infected and uninfected only). 

Files needed: 
1. 773 DEG list (2019-infection_DEGlist.tab) in project-crab/analyses
2. BLAST output from the crab transcriptome 
3. uniprot GO list (downloaded from uniprot.org)

```{r}
#install.packages("tidyverse")
library(tidyverse)
```

## Upload files
Upload DEG list:
I pasted list into excel in order to name the first column "Trinity_ID"
```{r}
degs <- read.table("../analyses/2019-DEGlist-infection-colnames.txt", header = TRUE)
head(degs)
```
Upload BLAST output from crab transcriptome: 
```{r}
blastout <- read.delim("../analyses/crab-blastout.txt", header = FALSE)
head(blastout)
```
Rename column "V3" --> "Entry" so that it matches the column name rom the uniprot ID list
```{r}
colnames()
```

Upload uniprot GO list:
```{r}
go <- read.delim("../data/uniprot-reviewed.tab", sep = '\t', header = TRUE)
head(go)
```

## Annotate blastout file with GO terms (downloaded from uniprot.org)
Join based on uniprot ID (Q)
















