---
title: "get-stress-gene-list"
output: html_document
---
Rmd to get the list of 5317 stress response genes that were identified using  https://github.com/RobertsLab/project-crab/blob/master/notebooks/042320-bairdi_transcriptome-BLAST-to-GOslim.ipynb.

Make a list of the genes that have the GOslim term "stress response" from the full, annotated crab transcriptome. List should be 5317 rows. 


```{r}
library(tidyverse)
library(dplyr)
```

Read in the table from the BLAST to GOslim jupter notebook linked above called "Blastquery-GOslim.tab". (file is saved locally on my computer)
```{r}
blastquery_goslim <- read.table("../analyses/Blastquery-GOslim.tab", sep = '\t')
head(blastquery_goslim)
```

Column "V3" is the GOslim terms. 
Call out the GOslim terms that have the word "stress" in them: 
```{r}
stress <- blastquery_goslim %>%
  filter(str_detect(V3, "stress"))
head(stress)
```

List is 5317 rows! Excellent!

Save list as is, and write it out to project-crab/analyses. May go back and get gene IDs if needed. 

Name columns first: 
```{r}
colnames(stress) <- c("Trinity_ID", "GO_ID", "GOslim", "Biological_process")
head(stress)
```

Write out table:
```{r}
write.table(stress, "../analyses/crab_stress-response-genes.tab", sep = '\t', quote = FALSE, row.names = FALSE)
```




