---
title: "which_degs_for_each_infection_status"
output: html_document
---
Rmd to figure out which of the DEGs (comparing infection status from the 2019 data set) are associated with each infection status (infected and uninfected)

```{r}
library(tidyverse)
library(dplyr)
```

Read in table of annotated DEGs
```{r}
degs <- read.table("../analyses/2019-DEGlist-infection-colnames.txt", header = TRUE)
head(degs)
```

Read in table of gene counts: 
```{r}
counts <- read.delim("https://raw.githubusercontent.com/sr320/nb-2020/master/C_bairdi/analyses/kallisto-0315.isoform.counts.matrix")
head(counts)
```

40,435 rows, 5 columns (Trinity ID plus the 4 samples)

Rename columns in 'counts'
329774 - infected (d12)
329775 - uninfected (d12)
329776 - infected (d26)
329777 - uninfected (d26)
```{r}
colnames(counts) <- c("Trinity_ID", "infected_12", "uninfected_12", "infected_26", "uninfected_26")
head(counts)
```

`join` the degs with counts based on column "Trinity_ID"
```{r}
degs_counts <- left_join(degs, counts, by = "Trinity_ID")
head(degs_counts)
```

positive log2fc --> deg in infected crabs
negative log2fc --> deg in uninfected crabs

Figure out how many degs are associated with each infection status: 
Infected
```{r}
infected <- filter(degs_counts, log2FoldChange > 0)
head(infected)
```
698 rows...

Uninfected
```{r}
uninfected <- filter(degs_counts, log2FoldChange < 0)
head(uninfected)
```

74 rows... 

Find the DEGs that are unique to each infection status: 










