---
title: "crab-hemat-GOslim"
output: github_document
---
Rmarkdown for creating visuals/analyses for crab and Hematodinium GOslim terms

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(data.table)
```

Read in crab-uniprot GOslim list:   
```{r}
crab <- read.table("../analyses/crab-Blastquery-GOslim.sorted", sep = '\t')
```

Get frequency of GOslim terms
```{r}
GOnumcrab <- aggregate(data.frame(count = crab$V2), list(value = crab$V2), length)
write.csv(GOnumcrab, "../analyses/crab-GOslim-count.csv")
```
Save stress response -related GO terms for crab:   
```{r}
stressGo <- filter(crab, crab$V2 == "stress response")
write.table(stressGo, "../analyses/crab-stress-genes.tab", quote = FALSE, sep = '\t', row.names = FALSE)
```
Join _blast-annot.tab (for crab) with crab stress genes to get Uniprot IDs
```{r}
bannot <- read.table("../analyses/_blast-annot.tab", sep = '\t')
bannotcol <- c("uniprot_ID", "Trinity_protein", "GO")
colnames(bannot) <- bannotcol
stresscol <- c("Trinity_protein", "GOterm")
colnames(stressGo) <- stresscol
unistress <- left_join(stressGo, bannot, by = "Trinity_protein")
write.table(unistress, "../analyses/crab-stress-uniprotID.tab", sep = '\t', quote = FALSE, row.names = FALSE)
```


Load hemat-Blastquery-GOslim.sorted (biological process)
```{r}
hemat <- read.table("../analyses/hemat-Blastquery-GOslim.sorted", sep = '\t')
```
Get frequency of GOslim terms
```{r}
GOnumhemat <- aggregate(data.frame(count = hemat$V2), list(value = hemat$V2), length)
write.csv(GOnumhemat, "../analyses/hemat-GOslim-count.csv")
```

Next steps: Open .csv's, get percentages of the frequency of GOslim terms, use googlesheets to create pie charts for Hematodinium and crab

---------------------------------------------------------------------------
THE REMAINDER OF SCRIPT IS FOR PLAYING AROUND WITH PIE CHARTS IN R
Rename columns
```{r}
crabcol <- c("GOslim", "count")
colnames(GOnumcrab) <- crabcol
```
Create pie chart
```{r}
labels <- GOnumcrab$GOslim
x <- GOnumcrab$count
piepercent<- round(100*x/sum(x), 1)
png(file = "crab-GO-perc-pie.jpg")
# Plot the chart.
pie(x, labels = piepercent, main = "Crab GOslim",col = rainbow(length(x)))
legend("topright", c("London","New York","Singapore","Mumbai", "x", "x", "x", "x", "x", "x", "x"), cex = 0.8, fill = rainbow(length(x)))

# Save the file.
dev.off()


```