---
title: "annotate-2019infection_status-DEGs"
output: html_document
---
Rmd to annotate the list of 772 DEGs comparing infected and uninfected crabs from the 2019 RNAseq dataset. DEG list created using `DESeq` by SR. 

```{r}
library(tidyverse)
library(dplyr)
```

Read in the list of DEGs:
```{r}
degs <- read.table("../analyses/2019-DEGlist-infection-colnames.txt", header = TRUE)
head(degs)
```

Read in the uniprot-SP-GO.sorted file:
```{r}
uniprot_sp_GO <- read.delim("http://owl.fish.washington.edu/halfshell/bu-alanine-wd/17-07-20/uniprot-SP-GO.sorted", sep = '\t', header = FALSE)
head(uniprot_sp_GO)
```


Rename some columns: 
```{r}
colnames(uniprot_sp_GO) <- c("uniprot_acc_ID", "entry_name", "review_status", "protein_name", "gene_name", "organism", "length", "V8", "V9", "V10", "V11", "gene_ontology_IDs")
head(uniprot_sp_GO)
```

Upload crab transcriptome BLAST output: 
```{r}
blastout <- read.delim("../analyses/BLAST_to_GOslim/_blast-sep.tab", sep = '\t', header = FALSE)
head(blastout)
```

Rename one column so that this file can be `join`-ed with the uniprot-SP-Go:
```{r}
colnames(blastout) <- c("Trinity_ID", "V2", "uniprot_acc_ID", "V4", "V5", "V6", "V7", "V8", "V9", "V10", "V11", "V12", "V13", "V14")
head(blastout)
```

`join` blastout and uniprot_sp_GO by "uniprot_acc_ID" column:
```{r}
blastout_uniprot <- left_join(blastout, uniprot_sp_GO, by = "uniprot_acc_ID")
head(blastout_uniprot)
```

same number of rows as the original blastout file... good to go.

`join` the annotated blast output file with degs by Trinity_ID:
```{r}
degs_annot <- left_join(degs, blastout_uniprot, by = "Trinity_ID")
head(degs_annot)
```


783 observations. 

Write out annotated DEG list to project-crab/analyses:
```{r}
write.table(degs_annot, "../analyses/degs_annot_2019-infection_status.tab", quote = FALSE, row.names = FALSE, sep = '\t')
```



