---
title: "sep_crab-hemat"
output: github_document
---

R markdown file to separate genes related to _Hematodinium_ and crabs.

Join uniprot-transcriptome BLASTx with dinoflagellate-transcriptome BLASTx

What doesn't match is crab. 
Create 2 tables: Hematodinium-related and Crab-related. 

*What DOES match, need to preserve and analyse* 

Get GOslim terms for each table separately, and dig deeper into genes separately (jupyter notebook). 

```{r}
library(dplyr)
library(tidyverse)
library(data.table)
```

Read in dinoflagellate-transcriptome BLAST output:
```{r}
dino <- read.table("http://owl.fish.washington.edu/scaphapoda/grace/PCSGA-2019/Cb_v1_blastx_uniprot2864_imac.tab", sep = '\t', header = FALSE)
```

Read in uniprot-transcriptome BLAST output: 
```{r}
uni <- read.csv("http://owl.fish.washington.edu/scaphapoda/grace/PCSGA-2019/1108-cbairdiblast-sprot.tab", sep = '\t', header = TRUE)
```

Rename columns
```{r}
blastcol <- c("Trinity_protein", "sseqid", "pident", "length", "mismatch", "gapopen", "qstart", "qend", "sstart", "send", "evalue", "bitscore")
colnames(dino) <- blastcol
colnames(uni) <- blastcol
```

anti_join tables based on Trinity_protein column
```{r}
crab <- anti_join(uni, dino, by = "Trinity_protein") %>% select(Trinity_protein, sseqid, evalue) %>% distinct()
```
```{r}
as_tibble(crab)
```

*get swiss-prot hits for dino!*
```{r}
hemat <- inner_join(uni, dino, by = "Trinity_protein") %>% select(Trinity_protein, sseqid.x, evalue.x) %>% distinct()
```
```{r}
as_tibble(hemat)
```

Check and make sure hemat and crab Trinity # are unique.
```{r}
inner_join(hemat, crab, by = "Trinity_protein")
```

Zero rows from inner_join ^ --> good to go!

Save crab and hemat separately into analyses
```{r}
write.table(crab,  quote = FALSE, sep = "\t", row.names=FALSE, "../analyses/crab-blastx-sp.tab")
write.table(hemat,  quote = FALSE,sep = "\t", row.names=FALSE, "../analyses/hemat-blastx-sp.tab")
```

Next step: use jupyter notebook to annotate dinoflagellate blastx output. 

