---
title: "sep_crab-hemat"
output: github_document
---

R markdown file to separate genes related to _Hematodinium_ and crabs.

Join uniprot-transcriptome BLAST with dinoflagellate-transcriptome BLAST

What doesn't match is crab. 
Create 2 tables: Hematodinium-related and Crab-related. 

Get GOslim terms for each table separately, and dig deeper into genes separately. 

```{r}
library(dplyr)
library(tidyverse)
library(data.table)
```

Read in dinoflagellate-transcriptome BLAST output:
```{r}
dino <- read.csv("../../../../Desktop/dino-blast-out.csv", header = FALSE)
```

Read in uniprot-transcriptome BLAST output: 
```{r}
uni <- read.csv("../../../GitHub/grace-Cbairdi-transcriptome/analyses/Blastquery-GOslim-sep.csv", header = TRUE)
```

Rename columns
```{r}
dcol <- c("Trinity_protein", "V2", "V3", "V4", "V5", "V6", "V7", "V8", "V9")
colnames(dino) <- dcol
```

Join tables based on trinity
```{r}
crab_genes <- anti_join(x = uni, y = dino, by = "Trinity_protein", copy = FALSE)
```

Save crab_genes and dino_genes separately

